Modalities for Location Virtualization

### 2022-09-20 programlogic.tex
movctl

To concretize the understanding of these principles achieved with the modal abstraction for address-space, $\modaldef\ell\modalP$, let us try to specify \textsf{movctl} in addition to the specifications of general \textsf{mov} instructions in Figure \fref{fig:reasoning}.

>>>>

To concretize the understanding of these principles achieved with the modal abstraction for address-space, $\modaldef\ell\modalP$, let us first investigate the specification of the instruction ($\textsf{movctl\_instr}$) switching address spaces. Assume that our CPU keeps the current address space based on its page table register CR3, as we see in Figure \fref{fig:addressspaceswitching}
\input{fig-ctlreasoning}
